---
title: "Analyzing App Categories and Sizes in Google Play Store"
author: "JH Pretorius"
date: "`r Sys.Date()`"
bibliography: Tex/ref.bib       
output:
  pagedown::html_paged:
    # template: wp_paged.html
    # css: ['wp.css', 'wp-fonts.css', 'wp-page.css']
    css: ["Template/default-fonts-Texevier.css", "Template/default-page-Texevier.css", "Template/default-Texevier.css"]
    csl: Template/harvard-stellenbosch-university.csl # referencing format used.
    template: ["Template/paged-Texevier.html"]

    toc: false
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: TRUE

---

```{r setup, include=FALSE}
#   Housekeeping
setwd("/Users/janhendrikpretorius/Library/CloudStorage/OneDrive-StellenboschUniversity/20713479-DatSci-Prac")
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
    #   Clear environment
rm(list = ls())
options(scipen = 999)

    #   Get external code
source("utilities/aesthetics.R") #  Get plot themes
source("utilities/convert_numeric.R")  # Convert multiple columns to numeric 
    #   Load libraries
pacman::p_load(dplyr, ggplot2, tidyverse, stringr, tidytext, ggridges, wordcloud2, ggmap, readxl, maps,
               viridis, lubridate, ggstream, modelsummary, gt, knitr, kableExtra, ggrepel, zoo, 
               rnaturalearth, rnaturalearthdata, sf, lwgeom)

    #   Load Data
path <- "data/googlePlay/"

file <- "googleplaystore_user_reviews.csv"
df_reviews <- read_csv(paste0(path, file))

file <- "googleplaystore.csv"
df_app <- read_csv(paste0(path, file))

```

\newpage

```{r data_cleaning}

# drop duplicates
df_reviews <- unique(df_reviews)
df_app <- unique(df_app)

# drop irrelevant columns (if any)
df_app <- df_app[ , !(names(df_app) %in% c('Current Ver', 'Android Ver'))]

df_reviews <- fill(df_reviews)  # fill forward
df_app <- na.omit(df_app)  # drop rows with missing values

df_app$'Last Updated' <- as.Date(df_app$'Last Updated', "%m/%d/%Y")

df_app$Installs <- gsub("[^0-9.]", "", df_app$Installs)  # Remove non-numeric characters
df_app$Installs <- as.numeric(df_app$Installs)  # Convert to numeric

df_app$Price <- gsub("[^0-9.]", "", df_app$Price)  # Remove non-numeric characters
df_app$Price <- as.numeric(df_app$Price)  # Convert to numeric

# Convert Size to numeric (in MB)
df_app$Size <- gsub("M", "", df_app$Size)  # Remove 'M'
df_app$Size <- ifelse(grepl("k", df_app$Size), as.numeric(gsub("k", "", df_app$Size))/1024, as.numeric(df_app$Size))  # Convert 'k' to 'M'


```

```{r visualisations, echo = FALSE, message = FALSE}

# Profit by category
profit_by_category <- df_app %>%
  group_by(Category) %>%
  summarise(Total_Revenue = mean(Price * Installs))

# Order categories by Total_Revenue
profit_by_category <- profit_by_category %>%
  arrange(Total_Revenue)

# Visualize profit by category as a lollipop plot
ggplot(profit_by_category, aes(x = Total_Revenue, y = reorder(Category, Total_Revenue))) +
  geom_point(size = 3, color = "#2AAA74") +
  geom_segment(aes(x = 0, xend = Total_Revenue, yend = reorder(Category, Total_Revenue)),
               color = "#2AAA74", size = 1) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8)) +
  xlab('Total Revenue') +
  ylab('Category')


```
The lollipop plot above shows the apps that generate the most revenue.

##      The analysis of the app data revealed some key insights:        {-}

Profit by Category: The analysis calculated the mean total revenue for each app category. The categories were ordered from lowest to highest total revenue. The lollipop plot displayed the total revenue for each category as individual points connected to the origin by line segments. This visualization allowed for a clear comparison of revenue across categories. Lifestyle, finance, family, weather, and game categories are the apps that tend to get the highest profits.

App Size by Category: The mean app size for each category was also calculated. However, the specific analysis and visualization for app size were not provided in the given code. It would be helpful to conduct a separate analysis to understand the average app size within each category. Game, family, sports, and travel categories tend to be the largest in size and all produce decent profits.

```{r size_table}
# Calculations
df_summary <- df_app %>%
  group_by(Category) %>%
  summarise(Mean_Size = mean(Size, na.rm = TRUE),
            Total_Revenue = mean(Price * Installs))

df_summary <- df_summary %>%
  arrange(desc(Mean_Size)) %>% 
    head(10)

# Create the table
gt_table <- df_summary %>%
  gt() %>%
  tab_header(
    title = "Mean App Size and Total Revenue by Category"
  ) %>%
  cols_label(
    Category = "Category",
    Mean_Size = "Mean App Size (MB)",
    Total_Revenue = "Mean Total Revenue"
  )

gt_table

```


